\proglang{collapse}: Advanced and Fast Statistical Computing and Data Transformation in \proglang{R}

### 2025-05-05 misc/JSS article/final/article.Rnw
Minors.

# Loading libraries and installing if unavailable
if(!requireNamespace("fastverse", quietly = TRUE)) install.packages("fastverse")
library(fastverse) # loads data.table, collapse, magrittr and kit (not used)
# Package versions used in the article:
# fastverse 0.3.4, collapse 2.1.2, data.table 1.17.0,
# bench 1.1.4, dplyr 1.1.4, tidyr 1.3.1, matrixStats 1.5.0
pkg <- c("bench", "dplyr", "tidyr", "matrixStats", "janitor")
if(!all(avail <- is_installed(pkg))) install.packages(pkg[!avail])

>>>>

# Loading libraries and installing if unavailable
if(!requireNamespace("fastverse", quietly = TRUE)) install.packages("fastverse")
library(fastverse) # loads data.table, collapse, magrittr and kit (not used)
# Package versions used in the article:
# fastverse 0.3.4, collapse 2.1.2, data.table 1.17.0,
# bench 1.1.4, dplyr 1.1.4, tidyr 1.3.1, matrixStats 1.5.0, janitor 2.2.0
pkg <- c("bench", "dplyr", "tidyr", "matrixStats", "janitor")
if(!all(avail <- is_installed(pkg))) install.packages(pkg[!avail])
